\documentclass[a4paper, 12pt]{report}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{pgfgantt}

\begin{document}
\subsection{Jan 4 Meeting}
Participants: Akio Ogawa, Oleg Tsai, Rahul Sharma, William Struble,  Weibin Zhang

Activity: We walked through the East platform, Bill showed us the tables on the 
platform that we can use and the crate for holding our electronics. 
Both sides of the beam pipe are available for the CALI installation. 
We decided to installed the CALI prototype on the north side due to less materials in front.

\subsection{Jan 19 Meeting}
Participants: Akio Ogawa, Oleg Tsai, William Struble, Timothy Camarda,  Weibin Zhang

Activity: We walked through the CALI installation, Tim was presented. We talked
about how to arrange the cables and measure how long the cable need to be. Tim
also told us what cable to use.

\subsection{Feb 8 Meeting}
Participants: Akio Ogawa, Oleg Tsai, Rahul Sharma, Weibin Zhang

Activity: Weibin presented the sketchup and pictures of the CALI prototype, discussing
what is going to be installed on the East platform. Rahul approved the installation.

\subsection{Feb 21 Meeting}
Participants: Rahul Sharma, William Struble, Weibin Zhang

Activity: We are ready to install the CALI protoype. Meet to discuss the possible
hazzards during the installation. We conclude that the possible hazzards are the usage
of ladder and lift. Rahul requires that every student involved should have the
ladder training, and Bill will help us in operating the lift. Meanwhile, Bill will
coordinate all activities, making sure the safety of the installation. Rahul approves
the plan.

\subsection{Feb 22-23: Installation}
Participants: William Struble, Weibin Zhang, Sean Preins, Peter Carney, Ryan Tsiao, Yousef Abdelkadous

Activity: Bill helps to lift all the iron blocks and tools, students only work on the platform and ground
to assemble the prototype and connect cables.
\end{document}
